Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

#clean data
asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing

#create a separate dataset for the records with >1 result
two_models <- asymptomaticQ2_2
two_models$author_1 <- gsub(",","",two_models$author_1)
#separate into 2 variables
two_models = two_models %>% 
  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
two_models = two_models %>% 
  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
two_models = two_models %>%
  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
two_models = two_models %>% 
  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";")

two_models <- two_models %>% #change values to numeric
  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
         q3_pp_m_2=as.numeric(q3_pp_m_2),
         q3_pp_l_1=as.numeric(q3_pp_l_1),
         q3_pp_l_2=as.numeric(q3_pp_l_2),
         q3_pp_u_1=as.numeric(q3_pp_u_1),
         q3_pp_u_2=as.numeric(q3_pp_u_2))

two_models <- two_models[!is.na(two_models$q3_pp_m_2),]

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

L1 <- two_models %>%
  pivot_longer(cols = c(6:7),
               names_to = "model",
               values_to = "q3_pp_m")

L1$label <- "Value"
for (i in 1:nrow(L1)) {
  if (L1$model[i] == "q3_pp_m_1") {
    sett <- L1$q3_setting_1[i]
  }else{
    sett <- L1$q3_setting_2[i]
  }
    L1$label[i] <- paste(L1$author_1[i], " [", sett, "]", sep = "")
  }
L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")

L2 <- two_models %>%
  pivot_longer(cols = c(8:9),
               names_to = "model",
               values_to = "q3_pp_l") %>%
  select("record_id", "model", "q3_pp_l", "author_1", "q3_setting_1", "q3_setting_2")

L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
L2$label <- "Value"
i = 1
for (i in 1:nrow(L2)) {
  if (L2$model[i] == "q3_pp_l_1") {
    sett -> L2$q3_setting_1[i]
  }else{
    sett -> L2$q3_setting_2[i]
  }
  L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
}

L2 <- L2 %>% select("q3_pp_l", "label")

L3 <- two_models %>%
  pivot_longer(cols = c(10:11),
               names_to = "model",
               values_to = "q3_pp_u") %>%
  select("record_id", "model", "q3_pp_u", "author_1", "q3_setting_1", "q3_setting_2")

L3$label <- "Value"
i = 1
for (i in 1:nrow(L3)) {
  if (L3$model[i] == "q3_pp_u_1") {
    sett -> L3$q3_setting_1[i]
  }else{
    sett -> L3$q3_setting_2[i]
  }
  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
}

L3$label2 <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")

L3 <- L3 %>% select("q3_pp_u", "label")

L4 <- two_models %>%
  pivot_longer(cols = c(13:14),
               names_to = "model",
               values_to = "setting") %>%
  select("record_id", "model", "setting", "author_1")
L4$label2 <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
L4$label <- paste(L4$author_1, " [", L4$setting, "]", sep = "")

L4 <- L4 %>% select("setting", "label")
#merge together
Lall <- merge(L2, L3, by = "label")   
Lall <- merge(Lall, L4, by = "label") 
Lall <- merge(Lall, L1, by = "label")
Lall <- Lall %>%
  select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
         "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
         "label")

#clean original dataset
asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
  mutate(setting = q3_setting)
asymptomaticQ2_2$q3_setting <- NULL
asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
attr(asymptomaticQ2_2, 'spec') <- NULL
str(asymptomaticQ2_2)
asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)

#add extra rows to original dataset
Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
#if q3_pp_m and q3_pa_m both NA then delete
Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]

#create new variable for all estimates and indicate asymp/presymp with new variable
#fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
Q2_2 <- Q2_2 %>%
  mutate(estimate = ifelse(!is.na(q3_pp_m),
                           q3_pp_m,
                           q3_pa_m),
         lower_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_l,
                                 q3_pa_l),
         upper_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_u,
                                 q3_pa_u),
         subgroup = ifelse(!is.na(q3_pp_m),
                           "presymp",
                           "asymp"))
#some records have presymp estimates in estimate now - must make new observation
both <- Q2_2 %>%
  filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
  mutate(estimate = q3_pa_m,
         lower_bound = q3_pa_l,
         upper_bound = q3_pa_u,
         subgroup = "asymp")
Q2_2 <- bind_rows(Q2_2, both)
#remove unnecessary cols
Q2_2 <- Q2_2 %>%
  select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
#round numbers to 2 decimal points
Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)

###############################################################
# forest plot

#prepare data
Q2_2_df <- Q2_2
#create label for proportions
Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
#create label for 95% CIs
Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
                     ";", Q2_2_df$CI_upper, "]", 
                     sep = "")
Q2_2_df <- Q2_2_df %>%
  mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
str(Q2_2_df)
#col to indicate headings/studies in plot
Q2_2_df$type <- 2
#new row for asymptomatic label in plot
Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
                          NA, NA, NA, NA, NA,1)
names(Asymp_label) <- names(Q2_2_df)
#new row for asymptomatic label in plot
Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
                            NA, NA, NA, NA, NA, 1)
names(Presymp_label) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
#font indicator
Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
str(Q2_2_df$fontface)

#arrange studies by subgroup
asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
               na.rm = TRUE) 
presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
                 na.rm = TRUE) 
Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
#new row for space in plot
space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
names(space) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, space)
Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
  filter(subgroup == "asymp") %>%
  mutate(line = 2:(asymp_n + 1))
Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
  filter(subgroup == "presymp") %>%
  mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
#join all rows again
Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)

#create forest plot
p <- ggplot() + 
  geom_point(data = Q2_2_df, #add estimates 
             aes(y = line, 
                 x = estimate),
             fill = "gray", 
             shape = 22, 
             color = "black",
             size = 4) +
  geom_errorbarh(data = Q2_2_df, #add error bars 
                 aes(y = line, 
                     xmin = lower_bound, 
                     xmax = upper_bound), 
                 height=0.3) +
  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
                x = c(-0.2, 1.05, 1.12), 
                label=c("Study", "Prop.", "95% CI")), 
            hjust = 0, 
            fontface = "bold") +
  geom_text(data = Q2_2_df, #add estimate labels
            aes(y = line, 
                x = 1.05, 
                label = prop), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add CI labels
            aes(y = line,
                x = 1.12,
                label = CI), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add study labels
            aes(y= line, 
                x=-0.2, 
                label = label,
                hjust = 0,
                fontface = fontface)) +
  theme_void() + #remove background
  scale_y_reverse() +
  geom_segment(data = Q2_2_df, #add line below point estimates
               aes(y = max(line) + 1, x = 0, xend = 1, 
                   yend = max(line) + 1)) +
  geom_segment(data = Q2_2_df, #add dash for 0
               aes(y = max(line) + 1, yend = max(line) + 1.3, 
                   x = 0, xend = 0)) +
  geom_segment(data = Q2_2_df, #add dash for 0.25
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x = 0.25, xend = 0.25)) +
  geom_segment(data = Q2_2_df, #add dash for 0.5
               aes(y = max(line)+1, yend=max(line) + 1.3,
                   x=0.5, xend=0.5)) +
  geom_segment(data = Q2_2_df, #add dash for 0.75
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x=0.75, xend = 0.75)) +
  geom_segment(data = Q2_2_df, #add dash for 1
               aes(y = max(line) + 1, 
                   yend = max(line) + 1.3,
                   x = 1, xend = 1)) +
  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
                x = 0:4/4,
                label = c(0, 0.25, 0.5, 0.75, 1))) +
  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5))

>>>>

############Old Codes###############
#clean data
# asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
# asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing
# 
# #create a separate dataset for the records with >1 result
# two_models <- asymptomaticQ2_2
# two_models$author_1 <- gsub(",","",two_models$author_1)
# #separate into 2 variables
# two_models = two_models %>% 
#   separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
# two_models = two_models %>% 
#   separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
# two_models = two_models %>%
#   separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
# two_models = two_models %>% 
#   separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";") 
# 
# two_models <- two_models %>% #change values to numeric
#   mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
#          q3_pp_m_2=as.numeric(q3_pp_m_2),
#          q3_pp_l_1=as.numeric(q3_pp_l_1),
#          q3_pp_l_2=as.numeric(q3_pp_l_2),
#          q3_pp_u_1=as.numeric(q3_pp_u_1),
#          q3_pp_u_2=as.numeric(q3_pp_u_2))
# 
# 
# two_models <- two_models[!is.na(two_models$q3_pp_m_2),]
# 
# substrRight <- function(x, n){
#   substr(x, nchar(x)-n+1, nchar(x))
# }
# 
# L1 <- two_models %>%
#   pivot_longer(cols = c(6:7),
#                names_to = "model",
#                values_to = "q3_pp_m") 
# 
# L1$label <- "Value"
# for (i in 1:nrow(L1)) {
#   if (L1$model[i] == "q3_pp_m_1") {
#   L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
#   }else{
#     L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
#   }
#   
# }
# 
# L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
# L2 <- two_models %>%
#   pivot_longer(cols = c(8:9),
#                names_to = "model",
#                values_to = "q3_pp_l") %>%
#   select("record_id", "model", "q3_pp_l", "author_1", "q3_setting_1", "q3_setting_2")
# 
# L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
# L2$label <- "Value"
# i = 1
# for (i in 1:nrow(L2)) {
#   if (L2$model[i] == "q3_pp_l_1") {
#     sett -> L2$q3_setting_1[i]
#   }else{
#     sett -> L2$q3_setting_2[i]
#   }
#   L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
# }
# 
# i=1
# for (i in 1:nrow(L2)) {
#   if (L2$model[i] == "q3_pp_l_1") {
#     L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
#   }else{
#     L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
#   }
#   
# }
# 
# L2 <- L2 %>% select("q3_pp_l", "label")
# L3 <- two_models %>%
#   pivot_longer(cols = c(10:11),
#                names_to = "model",
#                values_to = "q3_pp_u") %>%
#   select("record_id", "model", "q3_pp_u", "author_1", "q3_setting_1", "q3_setting_2")
# 
# L3$label <- "Value"
# i = 1
# for (i in 1:nrow(L3)) {
#   if (L3$model[i] == "q3_pp_u_1") {
#     L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
#   }else{
#     L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
#   }
#   
# }
# 
# L3$label2 <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
# 
# L3 <- L3 %>% select("q3_pp_u", "label")
# L4 <- two_models %>%
#   pivot_longer(cols = c(13:14),
#                names_to = "model",
#                values_to = "setting") %>%
#   select("record_id", "model", "setting", "author_1")
# L4$label2 <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
# L4$label <- paste(L4$author_1, " [", L4$setting, "]", sep = "")
# 
# L4 <- L4 %>% select("setting", "label")
# #merge together
# Lall <- merge(L2, L3, by = "label")   
# Lall <- merge(Lall, L4, by = "label") 
# Lall <- merge(Lall, L1, by = "label")
# Lall <- Lall %>%
#   select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
#          "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
#          "label")
# 
# #clean original dataset
# asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
# asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
#   mutate(setting = q3_setting)
# asymptomaticQ2_2$q3_setting <- NULL
# asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
# attr(asymptomaticQ2_2, 'spec') <- NULL
# str(asymptomaticQ2_2)
# asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
# asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
# asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)
# 
# #add extra rows to original dataset
# Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
# #if q3_pp_m and q3_pa_m both NA then delete
# Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]
# 
# #create new variable for all estimates and indicate asymp/presymp with new variable
# #fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
# Q2_2 <- Q2_2 %>%
#   mutate(estimate = ifelse(!is.na(q3_pp_m),
#                            q3_pp_m,
#                            q3_pa_m),
#          lower_bound = ifelse(!is.na(q3_pp_m),
#                                  q3_pp_l,
#                                  q3_pa_l),
#          upper_bound = ifelse(!is.na(q3_pp_m),
#                                  q3_pp_u,
#                                  q3_pa_u),
#          subgroup = ifelse(!is.na(q3_pp_m),
#                            "presymp",
#                            "asymp"))
# #some records have presymp estimates in estimate now - must make new observation
# both <- Q2_2 %>%
#   filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
#   mutate(estimate = q3_pa_m,
#          lower_bound = q3_pa_l,
#          upper_bound = q3_pa_u,
#          subgroup = "asymp")
# Q2_2 <- bind_rows(Q2_2, both)
# #remove unnecessary cols
# Q2_2 <- Q2_2 %>%
#   select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
# #round numbers to 2 decimal points
# Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
# Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
# Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)
# 
# ###############################################################
# # forest plot
# 
# 
# #prepare data
# Q2_2_df <- Q2_2
# #create label for proportions
# Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
# #create label for 95% CIs
# Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
# Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
# Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
#                      ";", Q2_2_df$CI_upper, "]", 
#                      sep = "")
# Q2_2_df <- Q2_2_df %>%
#   mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
# Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
# str(Q2_2_df)
# #col to indicate headings/studies in plot
# Q2_2_df$type <- 2
# #new row for asymptomatic label in plot
# Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
#                           NA, NA, NA, NA, NA,1)
# names(Asymp_label) <- names(Q2_2_df)
# #new row for asymptomatic label in plot
# Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
#                             NA, NA, NA, NA, NA, 1)
# names(Presymp_label) <- names(Q2_2_df)
# #add to exisiting dataframe
# Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
# #font indicator
# Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
# str(Q2_2_df$fontface)
# 
# #arrange studies by subgroup
# asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
#                na.rm = TRUE) 
# presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
#                  na.rm = TRUE) 
# Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
# #new row for space in plot
# space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
# names(space) <- names(Q2_2_df)
# #add to exisiting dataframe
# Q2_2_df <- rbind(Q2_2_df, space)
# Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
# Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
# Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
#   filter(subgroup == "asymp") %>%
#   mutate(line = 2:(asymp_n + 1))
# Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
#   filter(subgroup == "presymp") %>%
#   mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
# Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
# #join all rows again
# Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)
# 
# #create forest plot
# p <- ggplot() + 
#   geom_point(data = Q2_2_df, #add estimates 
#              aes(y = line, 
#                  x = estimate),
#              fill = "gray", 
#              shape = 22, 
#              color = "black",
#              size = 4) +
#   geom_errorbarh(data = Q2_2_df, #add error bars 
#                  aes(y = line, 
#                      xmin = lower_bound, 
#                      xmax = upper_bound), 
#                  height=0.3) +
#   geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
#                 x = c(-0.2, 1.05, 1.12), 
#                 label=c("Study", "Prop.", "95% CI")), 
#             hjust = 0, 
#             fontface = "bold") +
#   geom_text(data = Q2_2_df, #add estimate labels
#             aes(y = line, 
#                 x = 1.05, 
#                 label = prop), 
#             hjust = 0) +
#   geom_text(data = Q2_2_df, #add CI labels
#             aes(y = line,
#                 x = 1.12,
#                 label = CI), 
#             hjust = 0) +
#   geom_text(data = Q2_2_df, #add study labels
#             aes(y= line, 
#                 x=-0.2, 
#                 label = label,
#                 hjust = 0,
#                 fontface = fontface)) +
#   theme_void() + #remove background
#   scale_y_reverse() +
#   geom_segment(data = Q2_2_df, #add line below point estimates
#                aes(y = max(line) + 1, x = 0, xend = 1, 
#                    yend = max(line) + 1)) +
#   geom_segment(data = Q2_2_df, #add dash for 0
#                aes(y = max(line) + 1, yend = max(line) + 1.3, 
#                    x = 0, xend = 0)) +
#   geom_segment(data = Q2_2_df, #add dash for 0.25
#                aes(y = max(line) + 1, yend = max(line) + 1.3,
#                    x = 0.25, xend = 0.25)) +
#   geom_segment(data = Q2_2_df, #add dash for 0.5
#                aes(y = max(line)+1, yend=max(line) + 1.3,
#                    x=0.5, xend=0.5)) +
#   geom_segment(data = Q2_2_df, #add dash for 0.75
#                aes(y = max(line) + 1, yend = max(line) + 1.3,
#                    x=0.75, xend = 0.75)) +
#   geom_segment(data = Q2_2_df, #add dash for 1
#                aes(y = max(line) + 1, 
#                    yend = max(line) + 1.3,
#                    x = 1, xend = 1)) +
#   geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
#                 x = 0:4/4,
#                 label = c(0, 0.25, 0.5, 0.75, 1))) +
#   scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5))
